---
title: "Sobol_ODE"
output: html_document
authors: "Kristina Glass and Liane Chen"
date: "2024-05-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sensitivity)
library(tidyverse)
library(gridExtra)
library(purrr)
library(ggpubr)
library(deSolve)
```

##Implement model
Implement this model of forest growth (where forest size in measured in units of carbon (C))
  dC/dt = r ∗ C for forests where C is below a threshold canopy closure
  dC/dt = g ∗ (1 − C/K) for forests where carbon is at or above the threshold canopy closure

K is a carrying capacity in units of carbon, and e forest (C), Canopy closure threshold and carrying capacity are all in units of carbon

```{r}
source("growth.R")
```


```{r}
# Parameters
params <- list(
  pre_canopy_closure_rate = 0.01,
  post_canopy_closure_rate = 2,
  canopy_closure_threshold = 50,
  carrying_capacity = 250
)

# Initial condition
initial_forest_size <- 10

# Time span
time <- seq(0, 300, by = 1)

# Solve the ODE
ode <- ode(y = initial_forest_size, times = time, func = forest_growth, parms = params)

```


```{r}
# Graph the results
colnames(ode)=c("time","size")
ggplot(as.data.frame(ode),aes(time, size) )+geom_line() +
  labs(x = "Time (years)", y = "Forest Size (kgC)", title = "Forest Growth Model")
```


```{r}
# Define parameter distributions
parameter_means <- c(0.01, 2, 250, 50)
parameter_sds <- parameter_means * 0.1

# Number of samples
np <- 1000

# Generate samples for X1
set.seed(123)
r_samples <- rnorm(np, mean = 0.01, sd = 0.01 * 0.1)
g_samples <- rnorm(np, mean = 2, sd = 2 * 0.1)
K_samples <- rnorm(np, mean = 250, sd = 250 * 0.1)
canopy_samples <- rnorm(np, mean = 50, sd = 50 * 0.1)
X1 <- cbind.data.frame(r = r_samples, g = g_samples, K = K_samples, canopy_threshold = canopy_samples)

# Generate samples for X2
r_samples <- rnorm(np, mean = 0.01, sd = 0.01 * 0.1)
g_samples <- rnorm(np, mean = 2, sd = 2 * 0.1)
K_samples <- rnorm(np, mean = 250, sd = 250 * 0.1)
canopy_samples <- rnorm(np, mean = 50, sd = 50 * 0.1)
X2 <- cbind.data.frame(r = r_samples, g = g_samples, K = K_samples, canopy_threshold = canopy_samples)
```


```{r}
# Run Sobol sensitivity analysis using sobolSalt
sobol <- sobolSalt(model = NULL, X1, X2, nboot = 100)
```


```{r}
# Extract Sobol indices
S_indices <- sobol$S
T_indices <- sobol$T

# Convert Sobol indices to data frames for plotting
S_indices_df <- as.data.frame(S_indices)
T_indices_df <- as.data.frame(T_indices)

# Plot the first-order Sobol indices
ggplot(S_indices_df, aes(x = reorder(row.names(S_indices_df), original), y = original)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "First-Order Sobol Sensitivity Analysis",
       x = "Parameters",
       y = "First-Order Sensitivity Index (S)") +
  theme_minimal() +
  coord_flip()

# Plot the total Sobol indices
ggplot(T_indices_df, aes(x = reorder(row.names(T_indices_df), original), y = original)) +
  geom_bar(stat = "identity", fill = "red") +
  labs(title = "Total Sobol Sensitivity Analysis",
       x = "Parameters",
       y = "Total Sensitivity Index (T)") +
  theme_minimal() +
  coord_flip()

```


```{r}

```

